Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure - Supplementaty materials

### 2012-11-23 paper.tex
A bit closer towards reply to reviewers

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles. However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.

>>>>

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles. However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected. !!! Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nano particles. However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggest that the oscillations are not very dependent on the exact particle morphology.!!!

### 2012-11-23 supplementary.tex
A bit closer towards reply to reviewers

\section{The $\mu$-reactor platform}
The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0-2.5\,bar. The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.

\begin{figure}[h]
  \centering
  \includegraphics[width=8cm]{reactor.jpg}
  \caption{The Microreactor before the lid is anodically bonded to the reactor}
  \label{fgr:reactor}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue). The temperature is constant $210^\circ$C doing the entire measurement. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{figure*}

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment. The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations. The ratio between CO and CO$_2$ is drawn in black.}
  \label{fgr:duty_cycles_supplemental}
\end{figure}

>>>>

\section{The $\mu$-reactor platform}
The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume. The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar. The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure. The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.

\begin{figure}[h]
  \centering
  \includegraphics[width=8cm]{reactor.jpg}
  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
  \label{fgr:reactor}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=9cm]{oscil_gas_dependence_summary.png}
  \caption{Oscillation period (blue) as a function of time and CO concentration (black). The overall trend of increasing oscillation period with time is superimposed with small discontinuous steps when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=14cm]{oscil_gas_dependence.png}
  \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$ (blue). The temperature is constant at $210^\circ$C during the entire measurement. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{figure*}

@@

\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
  \caption{Running average of the CO and CO$_2$ concentrations and their ratio during a 4-day long experiment. The individual data-points is calculated as the integral of CO (red) or CO$_2$ (green) during the individual oscillation periods. The ratio between CO and CO$_2$ is drawn in black.}
  \label{fgr:duty_cycles_supplemental}
\end{figure}
